\section{Installation}
To install Chestnut Package Manager you need Python 2.4 or later installed on
your machine. Installation is very simple. Unpack the tar archive

\begin{verbatim}
tar xzvf Chestnut-2.1.0.tar.gz
\end{verbatim}

Then run the installation script

\begin{verbatim}
python setup.py install --home=$HOME
\end{verbatim}

Finally, set the following environment variables

\begin{verbatim}
export PATH="${PATH}:${HOME}/bin"
export PACKAGE_SEARCH_PATH=$HOME/ChestnutPkgs:/opt/ChestnutPkgs
\end{verbatim}

It is suggested that you add these lines into your \verb+.bash_profile+, so that they
get parsed every time you login.

The first line makes sure you have \verb+$HOME/bin+ in your \verb+PATH+ environment
variable. This line could be redundant, as this setting could already be
present in your system. Adding it twice does not really hurt.  After the
installation is done, you will have three executables in your \verb+$HOME/bin+
directory: \verb+cnrun+, \verb+cnls+ and \verb+cnpath+.

The second line specifies the directories where packages will be searched. A
possible choice for personal packages is \verb+$HOME/ChestnutPkgs+. You
can also have system-wide directories, for example in \verb+/opt/ChestnutPkgs+,
for example. Higher priority is given to the first directories in the list, and
lower priorities to the following ones (exactly as in \verb+PATH+). You are free to
add more if you want.

Finally you need to create the package directories. For the system-wide
directory, you need superuser privileges.  If you don't have superuser rights
on your system you can skip the creation of the system-wide directory and run
only the last command.

\begin{verbatim}
$ sudo mkdir -p /opt/ChestnutPkgs
$ sudo chmod 777 /opt/ChestnutPkgs
$ mkdir $HOME/ChestnutPkgs
\end{verbatim}

